---
title: "Workshop_scrap_R"
author: "Matt Steele"
date: '2022-03-15'
output: html_document
---

## Get and Set Working Directory ------------------------------------

```{r echo=FALSE}

# get working directory

  getwd()

# set working directory
  
  setwd()
  setwd("~/RWorkshop Development/workshop_scrape_twitter_R")
  
# you can set wd by using menu > session > set working directory > choose directory


```

=========================================================================

## Twitter API -------------------------------------------------------

    Documentation: https://developer.twitter.com/en/docs/twitter-api
    Dashboard: https://developer.twitter.com/en/portal/dashboard


==========================================================================

## Packages -----------------------------------------------------------

    ## Packages that you will need to have installed for this workshop

```{r}

install.packages("tidyverse")
install.packages("rtweet")
install.packages("ellipsis")
install.packages("pillar")
install.packages("tidygeocoder")
install.packages("hrbrthemes")
install.packages("glue")
install.packages("tidytext")
install.packages("wordcloud2")
install.packages("lubridate")
install.packages("textdata")


```

    ## Packages that you will need to load for this workshop

```{r message=FALSE}

library(tidyverse)
library(rtweet)
library(pillar)
library(tidygeocoder)
library(hrbrthemes)
library(glue)
library(tidytext)
library(wordcloud2)
library(lubridate)
library(textdata)

```

=====================================================================================

## Rtweet by ROpenSci ----------------------------------------------------------------

    Developers: https://ropensci.org/
    Documentation: https://docs.ropensci.org/rtweet/
    
======================================================================================

## Exportating Data

    
```{r}

help("write_delim") # readr package via tidyverse

write_csv(pk_following_info, "pkfollowers.csv")

```
    
    You can extract data using R and perform analysis and visualization functions in:
      - R
      - SAS
      - Python
      - STATA
      - SPSS

===========================================================================

## Create a Script to have R scrape Twitter at scheduled times  ---------------------------------------------------

If you're collecting data into the future, you may want to set your twitter API search to run on a schedule. 

Documentation and R Scripts

- Windows:  https://github.com/bnosac/taskscheduleR
- Linux: https://github.com/bnosac/cronR#cronr

```{r message=FALSE, warning=FALSE}

install.packages("taskscheduleR")
library(taskscheduleR)

```

===========================================================================

# Part I - Search Twitter ----------------------------------------------

## Function: search_tweets() ----------------------------------------------

    search twitter for tweets with search term(s) in them
    
    Boolean Operators
    
      AND operator (&)
      NOT operator (!) 
      OR operator (|)
      
```{r}

    help("search_tweets") # from the rtweet package

```
      
```{r}

ukraine_tweets <- search_tweets("ukraine", n=500, include_rts = F)
  View(ukraine_tweets)
  glimpse(ukraine_tweets)
  
  write_csv(ukraine_tweets, file = "ukraine_tweets.csv")
  
#Add BOOLEAN searches
  
ukraineWarTweets <- search_tweets(q = "ukraine & (war | conflict | invasion)", n = 3200, include_rts = F)
  ukraineWarTweets
  
# Search for mentions(@username) or hashtags(#hashtag)
  
navalny_mentioned <- search_tweets("@navalny", n = 3200, include_rts = F)
  navalny_mentioned


```

## Exercise - Search twitter for a term ------------------------------------------------------

```{r}

#Try it out for yourself - create an object and search twitter for a topic using search_tweets()

```

## Function: search_users()

        # Search Twitter for usernames with search term(s) in them
        

```{r}

help("search_users")

```

```{r}

freedom_names <- search_users("freedom", n = 1000)
   freedom_names %>% arrange(-retweet_count)
  freedom_names
  
```


=================================================================================


# Part II - Get followers of the account and accounts that are following an account -------

## Funtion: get_friends() -------------------------------------------------------

    locate an account and return who they are following
    
```{r}

    help("get_friends") # from the rtweet package

```
    
```{r}

# by name #

wvcbp_following <- get_friends("WVCBP", n = 2000)
  wvcbp_following

# by ID - https://tweeterid.com/ #

pk_following <- get_friends(users = "1221959101")
  pk_following


```


## Function: get_followers() -------------------------------------------------------------------------

    looks at an account and sees who is following it
    
```{r}

help("get_followers") # from the rtweet package

```

    
```{r}

# by name #

db_followers <- get_followers(user = 'doughboyspod')
  db_followers

# by ID - https://tweeterid.com/ #

pk_followers <- get_followers("1221959101", n = 5000) # we are going to limit for time sake
  pk_followers

```

## Function: lookup_users() -------------------------------------------------------------- 
      
      used with get_friends() to get more information on accounts being followed 
      
```{r}

help("lookup_users") # from the rtweet package

```
      
```{r}

# by following information

pk_following_info <- lookup_users(pk_following$user_id)
  pk_following_info

```
  
```{r}

# by followers information

pk_followers_info <- lookup_users(pk_followers$user_id)
  pk_followers_info

```

## Exercise - Get either the followers or users of a timeline ---------------------------------------
    
```{r}

# Create an object and find out an account's followers or friends get_followers() or get_friends()


```

```{r}

# Create an object and find out more about the followers/friends using lookup_users()
```

=============================================================================================

## Part III - Search Tweet Information ----------------------------------------------------


## Function: get_retweeters() --------------------------------------------------------------

      # Get the user_id of accounts that have retweeted a post

```{r}

help("get_retweeters") # from rtweet package

chicagoRiver_rters <- get_retweeters("1503324407581843457")
  chicagoRiver_rters
  

about_chicagoRiver_rters <- lookup_users(chicagoRiver_rters$user_id)
  about_chicagoRiver_rters

```


## Function: get_retweets() ---------------------------------------------------------------

        # Return information about the account that has retweeted a post. ~lookup_users()

```{r}

help("get_retweets") # from rtweet package

# The status ID of a tweet is in it's URL

# https://twitter.com/TVsCarlKinsella/status/1503324407581843457


```

```{r}

chicagoRiver_rt <- get_retweets("1503324407581843457")
  chicagoRiver_rt

```


=============================================================================================

## Part IV - Search User Information ------------------------------------------------------


## Function: get_favorites() ---------------------------------------------------------------

        # Get information on tweets that an account has favorited

```{r}

help("get_favorites") # from rtweet package

```

```{r}

dr_favorites <- get_favorites("david_j_roth", n = 3000)
  dr_favorites

```


## Function: get_timeline() ---------------------------------------------------------------

       # Get most recent post from a user's timeline

```{r}

help("get_timeline") # from the rtweet package

```

```{r}

# Phil Kabler's timeline 

pk_tln <- get_timeline(user = 'PhilKabler', n = 3200)
  pk_tln

```

    # Variables: see the variables in the data fram
    
```{r}

help("glimpse") # from the dplyr package

glimpse(pk_tln)

```

    # Plotting: what are the mid/max values for date
    
```{r}

pk_tln %>% 
  summarise(min(created_at), max(created_at))

```

## Function: ts_plot() -----------------------------------------------------------------

      allows you to plot the frequency of tweets and specify the time interval
      
      # Choose the Date format using the by function
        by = "secs", 
             "mins", 
             "hours", 
             "days", 
             "weeks", 
             "months"
             "years"
      
```{r}

## quick clean: change dttm to date

pk_tln$created_at <- as.Date(pk_tln$created_at) 

ts_plot()

```

```{r}

help("ts_plot") # from rwteet package

```

    # Visualize the data

```{r}

pk_tln %>% 
  dplyr::group_by(screen_name) %>%
  ts_plot("months", trim = 1L) + # choose by format
    ggplot2::geom_point() + geom_smooth() +
    ggplot2::labs(x = NULL, y= NULL, 
      title = "Frequency of Phil Kabler Tweets",
      subtitle = paste0(format(min(pk_tln$created_at), "%d %B %Y"),
                        " to ", format(max(pk_tln$created_at),"%d %B %Y")),
      caption = "Source: Data collected from Twitter's REST API via rtweet") +
    scale_x_datetime(date_labels = "%B", date_breaks = "1 month", minor_breaks = "1 week") +
    ggplot2::theme_minimal()

```

      # Get a "fancy" chart
        
```{r}

pk_tln_viz <- pk_tln %>% 
  dplyr::group_by(screen_name) %>%
  ts_plot("days", trim = 1L) + # change months to days
    ggplot2::geom_point(color = "coral") + # add some color
    geom_line(color = "darkseagreen") + # add some color
    hrbrthemes::theme_ipsum(grid = "Y") + # use themes from hrbr package
    ggplot2::theme(legend.position = "bottom",  #change text look, position and appearance
      legend.title = ggplot2::element_blank(), 
      plot.title = ggplot2::element_text(face = "bold", size = 28, color = "coral")) + 
    ggplot2::labs(x = NULL, y= NULL, 
      title = "Frequency of Phil Kabler Tweets",
      subtitle = paste0(format(min(pk_tln$created_at), "%d %B %Y"),
                        " to ", format(max(pk_tln$created_at),"%d %B %Y")),
      caption = "Source: Data collected from Twitter's REST API via rtweet") +
    scale_x_datetime(date_labels = "%b", date_breaks = "1 month") + # change date lables
    geom_smooth(color = "skyblue", se = 1)

ggsave(pk_tln_viz, filename = "pk_tln_viz.png")

```


## Exercise - Plot a timeline ---------------------------------------
    
```{r}

# Create a timeline for the account @dril (16298441)




# Find the min and max values




# Plot it




# Save it


ggsave(filename = "frq_tweets_dril.png")

```


====================================================================

## Part V - Get trending information ------------------------------

## Function: get_trends() ------------------------------------

    # Search for trends on twitter in a geographic area
    
```{r}

help("get_trends") # from rtweets package

```

```{r}
# by name

pitt_trend <- get_trends("Pittsburgh")
  pitt_trend

# by WOEID -> https://www.findmecity.com/index.html

italy_trend <- get_trends(woeid = 23424853)
  italy_trend

# by LAT and LNG

ukraine_trends <- get_trends(lat = 48.3794 , lng = 31.1656)
  ukraine_trends

```

## Visualize locations using tidygeocoder ----------------------------

```{r}

library(tidygeocoder)

```

```{r}

help("tidygeocoder")

```

## Function: geocode() ---------------------------------------------------------

    # retrieve the lat and lng
    
```{r}

help("geocode") # from tidygeocoder package

```

```{r}

# Retrieve timeline of the governor of West Virginia

wvGovernor_timeline <- get_timeline("WVGovernor", n = 6000)
  glimpse(wvGovernor_timeline) # place name variable
  

# Create a data frame of locations that the account has mentioned and get the coordinates
    
wvGovernor_places <- wvGovernor_timeline %>% 
  drop_na(place_name) %>% # remove NAs
  select(place_name:bbox_coords) %>% # select only variable from place_name to bbox_coords
  distinct() %>% # dplyr function that only select unique/distinct rows from a data frame
  mutate(addr = glue::glue("{place_full_name}, {country}")) %>%  # create a new variable using address
  tidygeocoder::geocode(addr, method = "osm") 

glimpse(wvGovernor_places)

```

## Visulize the data frame using maps from GGplot2 


```{r}

help("borders") # from ggplot2 package
help('coord_sf') # from ggplot2
help("geom_label_repel") # from ggrepel as part of ggplot2 package

```

```{r}

wvGovernor_places %>% 
  distinct() %>% 
  drop_na(lat) %>% 
  ggplot(aes(long, lat), color="grey99") +
  borders("state") +
  coord_sf (xlim = c(-85, -75), ylim = c(35, 42)) +
  geom_point(color = "goldenrod") +
  ggrepel::geom_label_repel(aes(label = place_full_name), 
                            segment.color = "goldenrod", segment.size = 1,
                            color = "navy",
                            max.overlaps = 20) + 
  theme_void()

```


